Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-07-05 related.tex
Modificado 3 de related works - Ready

% %
% For example, 
% 
% Me parece que aquí hay un error: Huang2010 es el survey, y sería mucha
% coincidencia que fuera lo mismo que el \citet{Glezakos2010} ¿o no?
%
% \cite{Huang2010} introduce a plant virus
% identification method based on neural networks with an evolutionary
% preprocessing stage, 
%

@@

\citet{Alves2011} used geoinformation techniques to
develop predictive models in the study of risk areas to soybean rust,
coffee leaf rust, and banana black Sigatoka, under consideration of
Brazil’s climatic characteristics and the distribution of soybean,
coffee and banana crops.
%
Temperature and rainfall data were acquired for the period from 1950
to 2000, and simulated data were generated for 2020, 2050 and 2080
using the SRES~A2 climate change scenarios.
%
Using principal components analysis, a single variable was generated
as a linear combination of 57 input variables, in order to determine
an index explaining 87\%, 88\% and 90\% of the data
%
\todofn{variability}{variabilidad de qué? - Comentario: de los datos de cada uno }  
%
of soybean, coffee and
banana crops, respectively, in municipal districts across Brazil.
%
The climatic model was used to generate the zoning of the three plant
diseases, using temperature and leaf wetness as input.
%
%Redunda con lo que sigue:
%Areas favorable for the diseases were plotted against the main coffee,
%soybean and banana growing areas in Brazil.
%
This methodology enabled the visualization of the changes in areas
favorable for epidemics under possible future scenarios of climate
change.
%
How intermediate result, they characterized the monociclic process of the black Sigatoka using  nonlinear regression. Although they do not present the detailed results, it no seem that they wanted to predict the progression of the black Sigatoka one, two or more periods ahead.

@@

@@

\TODO{Importantísimo es explicar aquí brevemente por qué esos otros
  trabajos no se aplican al caso de la Sigatoka, o qué es lo que han
  hecho mal, que este trabajo sí hace bien.}

>>>>

% %
% For example, 
% 
% Me parece que aquí hay un error: Huang2010 es el survey, y sería mucha
% coincidencia que fuera lo mismo que el \citet{Glezakos2010} ¿o no?
%
% \cite{Huang2010} introduce a plant virus
% identification method based on neural networks with an evolutionary
% preprocessing stage, 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Nota. la cita para lo de plant virus identificacion es  \citet{Glezakos2010}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\citet{Alves2011} used geoinformation techniques to
develop predictive models in the study of risk areas to soybean rust,
coffee leaf rust, and banana black Sigatoka, under consideration of
Brazil’s climatic characteristics and the distribution of soybean,
coffee and banana crops.
%
Temperature and rainfall data were acquired for the period from 1950
to 2000, and simulated data were generated for 2020, 2050 and 2080
using the SRES~A2 climate change scenarios.
%
Using principal components analysis, a single variable was generated
as a linear combination of 57 input variables, in order to determine
an index explaining 87\%, 88\% and 90\% of the data
%
\todofn{variability}{variabilidad de qué? - Comentario: de los datos de cada uno }  
%
of soybean, coffee and
banana crops, respectively, in municipal districts across Brazil.
%
The climatic model was used to generate the zoning of the three plant
diseases, using temperature and leaf wetness as input.
%
%Redunda con lo que sigue:
%Areas favorable for the diseases were plotted against the main coffee,
%soybean and banana growing areas in Brazil.
%
This methodology enabled the visualization of the changes in areas
favorable for epidemics under possible future scenarios of climate
change.
%
How intermediate result, they characterized the monociclic process of the black Sigatoka using  nonlinear regression. Although they do not present the detailed results, it no seem that they wanted to predict the progression of the black Sigatoka in one, two or more periods ahead, how we do.

@@

Although these studies have their contribution, none proposed the kind of preprocessing that we present, nor pose how to predict more than one period ahead without trying to predict climate.

@@

\TODO{Importantísimo es explicar aquí brevemente por qué esos otros
  trabajos no se aplican al caso de la Sigatoka, o qué es lo que han
  hecho mal, que este trabajo sí hace bien. - Modificado}
